Twisted \(M\)-theory and its perturbative quantization.

### 2023-02-07 revisions/response/response.tex

\documentclass{amsart}

\usepackage{macros-mtheory}

\begin{document}

\title{Response to referee report \\ ``Twisted eleven-dimensional supergravity''}

\maketitle

We want to express our deep gratitude to the referee for the report on our manuscript. We believe that the referee's suggestions greatly improved the readability and clarity of our results and we hope that shows in the revised work.

Below, we summarize the edits that have been made to address the referee's suggestions.

\subsection*{Edits}
\begin{enumerate}
\item The referee asked why only the extension corresponding to the M2 brane is discussed in section 3.2. We have added a remark to address this at the end of section 3. \\

\item The referee requested elaboration on page 24, in the proof of proposition 3.6, in showing that the bracket between odd elements in the $Q$-twisted M2 brane algebra is compatible with the bracket induced by the cubic term in the action. We have added a paragraph in the proof of proposition 3.6 to address this.
\end{enumerate}

\subsection*{Clarifications}
\begin{enumerate}
\item The referee requested clarifications about the intuition and motivation which led us to study the model in the manuscript. This is stated both in the abstract and in the paragraph preceding Conjecture 0.1 on page 3. \\

\item The referee suggested that we formulate a conjecture relating $E(5|10)$ to shifted truncated Yangians. Though a detailed conjecture in this direction is outside of the scope of the submitted manuscript, we wish to point out that steps in this direction appear in follow-up work by the first and last author (see the introduction of \cite{RW22}). There, the authors amass character-level evidence for the claim that the M5 brane algebra in the minimal twist admits a deformation to the $\mathcal{W}_{1+\infty}$ algebra.

\end{enumerate}

\begin{thebibliography}{9}
\bibitem{RW22}
	S. Raghavendran and B. Williams,
	\textit{A holographic approach to the six-dimensional superconformal index},
	\url{arXiv:2210.07910},
	2022.

\end{thebibliography}

\end{document}

### 2023-02-07 fivebranes/membrane.tex

>>>>

\subsection{Operators on a single membrane}

\begin{prop}
\label{prop:3done}
The local character $\chi_{\lie{u}(1)}(q,t_1,t_2,r)$ of the holomorphic twist of the theory on a single membrane is given by the plethystic exponential of the single particle index
\beqn\label{eqn:3done}
f^{3d}_{\lie{u}(1)} (t_1,t_2,t_3,q) = \frac{q^{1/4} (t_1+t_2+t_3+ (t_1 t_2 t_3)^{-1}) - q^{3/4} (t_1^{-1} + t_2^{-1} + t_3^{-1} + t_1 t_2 t_3)}{1-q} .
\eeqn
\end{prop}

This agrees with the membrane index computed in \cite[Equation (2.31)]{Bhattacharya:2008zy}.

\subsection{A conjectural description for the theory two membranes}

\begin{prop} \label{prop:3dtwo}
The character of local operators of the factorization algebra $\clie_\bu(\cG_{2,c})$ on $\C^3$ is given by the following expression
\begin{multline}\label{eqn:3dtwo1}
(1-q) f^{3d}_{\lie{sl}(2)}(t_1,t_2,t_3,q) = q^2 + q (\chi_{\C^4}(t) \chi_{\C^4}(t^{-1}) - 1) \\ - q^{3/2} \frac12 (\chi_{\C^4}(t)^2 - \chi_{\C^4}(t^2)) - q^{1/2} \frac12 (\chi_{\C^4}(t)^2 + \chi_{\C^4}(t^2))
\end{multline}
\end{prop}

The Higgs and Coloumb branch specializations are given by 
\beqn
t_1 t_2 = q^{\pm 1/2} .
\eeqn
This results in the following expression
\beqn
f^{3d}_{\lie{sl}(2)}|_{t_1 t_2 = q^{\pm 1/2}} = q^{-1/2} t_1^{-2} + 1 + q^{1/2} t_1^2 .
\eeqn

\subsection{The membrane decomposition}

We briefly highlight an analogous construction of the restricted factorization algebra describing membranes.
Recall that in the twist we are considering the worldvolume theory of membranes is a three-dimensional partially topological-holomorphic field theory which exist on a product $\R \times C$ where $C$ is a Riemann surface.

We consider the eleven-dimensional theory on $\R \times X_C$ where $X_C$ is the Calabi--Yau fivefold
\[
X_C = \text{Tot}(K_C^{1/4} \otimes \C^4),
\]
the total space of the rank four bundle $K_C^{1/4} \otimes \C^4$ over $C$.
Denote by 
\[
\pi \colon V \to \R \times C
\] 
the pullback of this vector bundle along the projection $\R \times C \to C$.
We can equivalently think of the eleven-manifold as the total space of the bundle $V$ over $\R \times C$. 
In this description, the twisted membranes will be supported along the zero section of $V$. 
The factorization algebra $\Obs_{sugra}$ on ${\rm Tot}(V)$ can be pushed forward along $\pi$ to a factorization algebra $\pi_* \Obs_{sugra}$ on $\R \times C$.

As in the fivebrane case, this is not the factorization algebra associated to an ordinary field theory on $\R \times C$.
Nevertheless there is a subfactorization algebra $\Bar{\pi}_* \Obs_{sugra}$ which admits a natural grading so that each filtered component can be understood as such.

To construct this factorization algebra we consider the action of the compact torus $U(1)^{\times 4}$ which rotates the fibers of the bundle $K_C^{1/4} \otimes \C^4$.
We let $\Bar{\pi}_* \Obs_{sugra}$ be the factorization algebra on $\R \times C$ consisting of observables which are finite sums of integral eigenvectors for this group action.
Again, we find that $\Bar{\pi}_* \Obs_{sugra}$ is of the form $\clie^\bu(\cG_{\R \times C})$ for some $\infty$ sheaf of $L_\infty$ algebras $\cG_{\R \times C}$ on $\R \times C$ which is the sections of a pro vector bundle.

Analogous to the decomposition determined by the $\C^\times$ action considered in \ref{s:cstarfive}, there is a decomposition of $\cG_{\R \times C}$ determined by a (different) $\C^\times$ acting on the fields of the eleven-dimensional theory on ${\rm Tot}(V) \cong \R \times X_C$.

In a local THF chart $U \subset \R \times C$ we can write a generic field of the eleven-dimensional theory on $\pi^{-1} U$ in coordinates as $f(t;z,w)$ where $(t;z) \in U \subset\R \times C$ is THF coordinate and $w=(w_1,w_2,w_3,w_4)$ is the holomorphic fiber coordinate of the rank four bundle $V$.

%For simplicity let us consider the eleven-dimensional theory on flat space $\R \times \C^5$ with some number of fivebranes supported on
%\[
%0 \times 0 \times \C^3 \subset \C^5 .
%\]
%is that (after taking into account the backreaction) the observables on a large number of fivebranes is Koszul dual to the factorization algebra 
%
%\parsec[s:flatdecomp]
%
%%In the simple case where $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ then the manifold obtained by removing the locus of the brane is homeomorphic to
%%\[
%%\C^3 \times (\R \times \C^2 - 0) .
%%\]
%%
%%Let $\pi \colon \R \times \C^5 - (0 \times \C^3) \to \C^3 \times \R_{>0}$ be the projection map whose fibers are homeomorphic to the sphere $S^4$ which links the location of the fivebranes.
%%We restrict the factorization algebra of the eleven dimensional theory $\Obs_{sugra}$ to the open set obtained by removing the locus of the brane.
%
%In the simple case that $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ there is a more direct construction of the factorization algebra $\Obs_{sugra}|_{Z}$. 
%
%Let $\pi \colon \R \times \C^5 \to \C^3$ be the projection map.
%Then, via $\pi$ we can pushforward the factorization algebra associated to the eleven-dimensional theory to obtain a factorization algebra
%\[
%\pi_* \Obs_{sugra} 
%\]
%on $\C^3$.
%This factorization algebra is not the factorization algebra associated to an ordinary sort of field theory on $\C^3$. 
%Nevertheless there is a subfactorization algebra which admits a natural grading so that each filtered component can be understood as such.

With this notation in place, we introduce the following $\C^\times$ action on the fields of the eleven-dimensional theory:
\begin{itemize}
\item On the fields $\mu(t;w,z)$ the action is
\[
\lambda \cdot \mu(t;z,w) = \mu(t; z , \lambda w).
\]
\item On the fields $\nu(t;w,z)$ the action is
\[
\lambda \cdot \nu(t;z,w) = \nu(t;z ,\lambda w).
\]
\item On the fields $\beta(t;w,z)$ the action is
\[
\lambda \cdot \beta(t;z,w) = \lambda^{-2} \beta(t; z, \lambda w).
\]
\item On the fields $\gamma(t;w,z)$ the action is
\[
\lambda \cdot \gamma(t;z,w) = \lambda^{-2} \gamma(t; z ,\lambda w).
\]
\end{itemize}

\begin{prop}
The $L_\infty$ structure on $\cL_{sugra}$ is equivariant for this $\C^\times$ action. 
%The odd symplectic form on $\cL_{sugra}$ is weight $-1$ for this $\C^\times$ action. 
\end{prop}

As in the case of fivebranes, this proposition allows us to decompose the local Lie algebra $\cG_{\R \times C}$ into weights. 
Similarly as above one can show that the $n$th eigenspace is quasi-isomorphic to a local Lie algebra of the form
\[
\Omega^\bu(\R) \otimes \Omega^{0,\bu}\left(C, \cV^{(n)}\right)
\]
where $\cV^{(n)}$ is a holomorphic super vector bundle on $C$.

We will state explicit descriptions of the first few eigenspaces without details of the proof. 
The weight decomposition is concentrated in degrees $\geq -2$. 
The lowest weight $n=-2$ is not very interesting, it is quasi-isomorphic just to the de Rham complex 
\beqn
\Omega^\bu (\R) \otimes \Omega^{\bu, \bu}(\C) \simeq \Omega^\bu (\R^3) .
\eeqn

The next nontrivial eigenspace is $n=-1$. 
Here, one can see that 
\[
\cV^{(-1)} \simeq K_{C}^{1/4} \otimes \C^4 \oplus \Pi K^{3/4}_C \otimes \C^4 .
\]
For $n=0$ one has 
\[
\cV^{(0)} \simeq \T_C \oplus \lie{sl}(4) \otimes \cO_C \oplus \Pi \left(K^{-1/2}_C \otimes \wedge^2 \C^4 \oplus K^{-1/2}_C \otimes S^2 \C^4\right) .
\]
As in the case of fivebranes, the $n=0$ eigenspace is equipped with the structure of a super Lie algebra whose exact form we do not state now.

### 2023-02-07 g2twist.tex

There are two types of interactions in the original theory.
The first is
\begin{equation}\label{eqn:int1}
  \frac12 \int_{X\times Z \times L} \frac{1}{1-\nu} \left(\del \gamma \vee \mu^2 \right) \wedge (\omega_Z \wedge \Omega_X)
\end{equation}
and the second is
\begin{equation} \label{eqn:int2}
  \frac16\int_{X \times Z \times L} \frac{1}{1-\nu} \gamma \partial \gamma \partial \gamma .
\end{equation}

@@

Next, we expand Equation (\ref{eqn:int2}) around $\gamma \to \Tilde{\gamma} = \gamma + \delta \gamma^{1,0}$.
This is
\[
  \frac16 \int \frac{1}{1-\nu} \gamma \partial \gamma \partial \gamma + \frac{\delta}{2} \int \frac{1}{1-\nu} \left(\gamma \partial \gamma\right) \wedge \omega_Z .
\]
Notice that there are no $\delta^2$ terms since $\partial \gamma^{1,0} \partial \gamma^{1,0} = 0$.
Again, we further expand this into holomorphic components along $X,Z$:
\begin{multline}
\frac16 \int \frac{1}{1-\nu} \left(\gamma_X \partial^Z \gamma_X \partial^Z \gamma_X +\gamma_X \partial^X \gamma_X \partial^Z \gamma_Z +  \gamma_X \partial^X \gamma_Z \partial^X \gamma_Z \right)
\\
\frac{\delta}{2} \int \frac{1}{1-\nu} \left(\gamma_X \partial^X \gamma_X \right) \wedge \omega_Z 
\label{eqn:delta2}
\end{multline}

@@

We identify this linear BRST complex, up to quasi-isomorphism, with a smaller BRST complex. 
Consider the complex
\beqn
\Omega^{0,\bu}_Z \hotimes \Omega^{\bu,\bu}_X \hotimes \Omega^\bu_L = \oplus_{k =0}^3 \Omega^{0,\bu}_Z \hotimes \Omega^{k,\bu}_X \hotimes \Omega^\bu_L [-k] 
\eeqn
which is equipped with the differential $\dbar^Z + \dbar^X + \del^X + \d^L_{\dR}$. 
Write $\alpha = \alpha^0 + \cdots + \alpha^3$ for a field in this complex, using the decomposition on the right hand side.

There is a map from this smaller BRST complex to the original defined by the following equations 
\begin{multline}
\mu_Z = \omega_Z^{-1} \del^Z \alpha^0, \quad \mu_X = \Omega_X^{-1} \alpha^2, \quad \nu = \Omega_X^{-1} \alpha^3 \\
\beta = \alpha^0, \quad \gamma_X = \alpha^1 , \quad \gamma_Z = 0 .
\end{multline}
This map is a quasi-isomorphism of linear BRST complexes.

Restricting the deformed BV action $I(\gamma+\gamma^{1,0})$ along this map we obtain a new interaction $\Tilde{I}(\alpha)$. 
It has the following form
\begin{multline}
\int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \left(\frac12 \del^X \alpha^1  [ \alpha^2 \vee (\alpha^2 \vee \Omega_X^{-1})] + \alpha^2 \del^Z \alpha^1 \del^Z \alpha^0\right) \\
+ \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \alpha^1 \partial^Z \alpha^1 \partial^Z \alpha^1 \\ + \frac{\delta}{2} \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \alpha^3 \partial^Z \alpha^0 \partial^Z \alpha^0 + \frac{\delta}{2} \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \partial^X \alpha^1 (\alpha^1 \Omega^{-1}_X \alpha^3) .
\end{multline}

@@

Next, we compute
\[
\{I_{CS}, K\} = \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} [\alpha \vee (\alpha \vee \Omega^{-1}_Z)] \{\alpha,\alpha\} 
\]
which is the second term in \eqref{eqn:Iprime}. 
\end{proof}
\end{proof}
\end{document}

>>>>

In addition to the kinetic terms, there are two types of interactions in the original theory.
The first is
\begin{equation}\label{eqn:int1}
  \frac12 \int_{X\times Z \times L} \frac{1}{1-\nu} \left(\del \gamma \vee \mu^2 \right) \wedge (\omega_Z \wedge \Omega_X)
\end{equation}
and the second is
\begin{equation} \label{eqn:int2}
  \frac16\int_{X \times Z \times L} \gamma \partial \gamma \partial \gamma .
\end{equation}

@@

Next, we expand Equation (\ref{eqn:int2}) around $\gamma \to \Tilde{\gamma} = \gamma + \delta \gamma^{1,0}$.
This is
\[
  \frac16 \int \gamma \partial \gamma \partial \gamma + \frac{\delta}{2} \int \left(\gamma \partial \gamma\right) \wedge \omega_Z .
\]
Notice that there are no $\delta^2$ terms since $\partial \gamma^{1,0} \partial \gamma^{1,0} = 0$.
Again, we further expand this into holomorphic components along $X,Z$:
\begin{multline}
\frac16 \int \left(\gamma_X \partial^Z \gamma_X \partial^Z \gamma_X +\gamma_X \partial^X \gamma_X \partial^Z \gamma_Z +  \gamma_X \partial^X \gamma_Z \partial^X \gamma_Z \right)
\\
+ \frac{\delta}{2} \int \left(\gamma_X \partial^X \gamma_X \right) \wedge \omega_Z 
\label{eqn:delta2}
\end{multline}

@@

We replace this linear BRST complex, up to quasi-isomorphism, with a smaller BRST complex. 
Consider the complex
\beqn
\Omega^{0,\bu}_Z \hotimes \Omega^{\bu,\bu}_X \hotimes \Omega^\bu_L = \oplus_{k =0}^3 \Omega^{0,\bu}_Z \hotimes \Omega^{k,\bu}_X \hotimes \Omega^\bu_L [-k] 
\eeqn
which is equipped with the differential $\dbar^Z + \dbar^X + \del^X + \d^L_{\dR}$. 
Write $\alpha = \alpha^0 + \cdots + \alpha^3$ for a field in this complex, using the decomposition on the right hand side.

There is a non-linear map of BRST complexes from this one to the original one defined by the following equations 
\begin{multline}
\mu_Z = e^{-\til{\alpha}^3} \omega_Z^{-1} \del^Z \alpha^0, \quad \mu_X = e^{-\til{\alpha}^3} \Omega_X^{-1} \alpha^2, \quad \nu = e^{-\til{\alpha}^3} \til{\alpha}^3 \\
\beta = e^{\til{\alpha}^3} (\alpha^0 + \Omega_X^{-1} \alpha^1 \alpha^2), \quad \gamma_X = e^{\til{\alpha}^3} \alpha^1 , \quad \gamma_Z = 0 .
\label{eqn:g2map}
\end{multline}
In the above equation we have introduced the notation $\til{\alpha}^3 = \Omega_X^{-1} \vee \alpha^3$. 
The induced map of linear BRST complexes is a quasi-isomorphism. 
We show that the full non-linear map intertwines the action functionals and hence defines an equivalence of BV theories.

The restriction of the kinetic term $\beta \div \mu$ along \eqref{eqn:g2map} is
\beqn
\alpha^0 \alpha^2 \del^X \til{\alpha}^3 + \alpha^1 (\alpha^2)^2 \del^X \til{\alpha}^3 + \alpha^0 \del^X \alpha^2 + \alpha^1 \alpha^2 \del^X \alpha^2 .
\eeqn

Restricting the action \eqref{eqn:delta1} along the map \eqref{eqn:g2map} we obtain
\begin{multline}
\frac12 \alpha^1 (\alpha^2)^2 \del^X \til{\alpha}^3 + \frac12 \del^X \alpha^1 (\alpha^2)^2 
\end{multline}

\begin{multline}
\int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \left(\frac12 \del^X \alpha^1  [ \alpha^2 \vee (\alpha^2 \vee \Omega_X^{-1})] + \alpha^2 \del^Z \alpha^1 \del^Z \alpha^0\right) \\
+ \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \alpha^1 \partial^Z \alpha^1 \partial^Z \alpha^1 \\ + \frac{\delta}{2} \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \alpha^3 \partial^Z \alpha^0 \partial^Z \alpha^0 + \frac{\delta}{2} \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \partial^X \alpha^1 (\alpha^1 \Omega^{-1}_X \alpha^3) .
\end{multline}

@@

Next, we compute
\[
\{I_{CS}, K\} = \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} [\alpha \vee (\alpha \vee \Omega^{-1}_X)] \{\alpha,\alpha\} 
\]
which is the second term in \eqref{eqn:Iprime}. 
\end{proof}
\end{proof}
\end{document}
